\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-16 jasa/paper-jasa.tex
Should be good now? :s

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig1a.pdf}
        \caption{$p(\mathbf{x}|\gamma)$  for $\gamma=0.05$ and $\gamma=0$}
        \label{fig:1a}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
      %(or a blank line to force the subfigure onto a new line)
%    \begin{subfigure}[b]{0.45\textwidth}
%        \includegraphics[width=\textwidth]{figures/fig1b.pdf}
%        \caption{Linear model}
%        \label{fig:1b}
%    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \hspace{-.2em}\includegraphics[width=1.10\textwidth]{figures/fig1b.pdf}
        \caption{$\hat{p}_c(\hat{s}_{c,c^\prime}(\mathbf{x}) )$ and $1/(1+\hat{r}(\hat{s}_{c,c^\prime}(\mathbf{x}))$}
        \label{fig:p_sij}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-ratio-dist.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x}))) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig-likelihood.pdf}
        \caption{$-2\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

@@

    \begin{subfigure}[t]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2a.pdf}
        \caption{True MLEs vs. approximated MLEs.}
        \label{fig:2a}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2b.pdf}
        \caption{$p(-2 \log \Lambda(\gamma=0.05) \, | \, \gamma=0.05)$}
        \label{fig:2b}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6a}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6b}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6d}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/likelihood_comp_2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6e}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/ROC_comp2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6f}
    \end{subfigure}

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig1a.pdf}
        \caption{$p(\mathbf{x}|\gamma)$  for $\gamma=0.05$ and $\gamma=0$}
        \label{fig:1a}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig1b.pdf}
        \caption{$\hat{p}_c(\hat{s}_{c,c^\prime}(\mathbf{x}) )$ and $1/(1+\hat{r}(\hat{s}_{c,c^\prime}(\mathbf{x}))$}
        \label{fig:p_sij}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig1e.pdf}
        \caption{$p( \log \hat r(\hat{s}(\mathbf{x}))) \, | \,\gamma = 0.05)$ }
        \label{fig:decomposed_ratio}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig1f.pdf}
        \caption{$-2\log \Lambda(\gamma)$ }
        \label{fig:likelihood}
    \end{subfigure}

@@

    \begin{subfigure}[t]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2a.pdf}
        \caption{Exact vs. approximated MLEs.}
        \label{fig:2a}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.4\textwidth}
        \includegraphics[width=\textwidth]{figures/fig2b.pdf}
        \caption{$p(-2 \log \Lambda(\gamma=0.05) \, | \, \gamma=0.05)$}
        \label{fig:2b}
    \end{subfigure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=10.075em]{figures/likelihood_comp_0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6a}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=9.5em]{figures/ROC_comp0.pdf}
        \caption{Poorly trained, well calibrated. }
        \label{fig:6b}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=10.075em]{figures/likelihood_comp_1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6c}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=9.5em]{figures/ROC_comp1.pdf}
        \caption{Poorly calibrated, well trained. }
        \label{fig:6d}
    \end{subfigure}

    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=10.075em]{figures/likelihood_comp_2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6e}
    \end{subfigure}
    ~
    \begin{subfigure}[t]{0.4\textwidth}
        \centering
        \includegraphics[height=9.5em]{figures/ROC_comp2.pdf}
        \caption{Well trained, well calibrated. }
        \label{fig:6f}
    \end{subfigure}
